Better Splitting Algorithms for Parallel Corpus Processing

### 2012-08-09 doc/latex/paper.tex
Made changes required by Ondrej for the paper to compile at the journal.

\documentclass{pbml}
\usepackage{natbib}
\usepackage{thanks-nostar}
\usepackage{subfig}
%\setlength\titlebox{3in}
%\usepackage{naaclhlt2010}
%\usepackage{draftcopy}[all,draft,light,timestamp]
%\usepackage{draftwatermark}
%\usepackage{datetime}
%\usepackage{times}
%\usepackage{latexsym}
%\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
\newcommand\bmmax{1}
\usepackage{bm}
\usepackage{fontspec}
%\usepackage{todonotes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[colorlinks,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{
width=7cm,
compat=1.3,
colormap name=blackwhite
%,bar cycle list name=black white
}
%\SetWatermarkLightness{0.95}
%\SetWatermarkLightness{1}
%\SetWatermarkText{\dmyydate \today, \currenttime}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\begin{figure*}[!p]
\centering
\subfloat[Algorithm \ref{alg:naive} --- \textsc{Naive-Split}]{
\begin{tikzpicture}
\begin{axis}[
xmode=normal,
ymode=normal,
xtick={0,8,16,24,32,40,48,56,64},%data,%{100,200,300,400,500,600,700,800},
ytick={0,10,20,30,40,50,60,70,80},
tick label style={font=\tiny},
%xlabel=Split Part Number,
ylabel=Translation Time,
ymin=0,
ymax=80,
xmin=0,
xmax=64,
xtick pos=left,
ytick pos=left,
xtick align=outside,
ytick align=outside,
ybar,
bar width=5pt,
cycle list={fill=black},
width=13cm,
height=4cm
]
%\input{split/time_sum.64}
\input{figures/parts_time_summary/Algorithm.naive+Corpus.nist08_dev+Parts.64/plot.tex}
\end{axis}
\end{tikzpicture}
%\caption{Total time (in seconds) for each part when split using Algorithm \ref{alg:naive}.}
%\caption{Translation decoding time (in seconds) of sentences from the NIST OpenMT 2008 Urdu-English task with a decoder configured using a 5-gram language model.}
\label{fig:plot-naive}
%\end{figure*}
}

\subfloat[Algorithm \ref{alg:histogram} --- \textsc{Histogram-Split}]{
%\begin{figure*}[!p]
%\centering
\begin{tikzpicture}
\begin{axis}[
xmode=normal,
ymode=normal,
xtick={0,8,16,24,32,40,48,56,64},%data,%{100,200,300,400,500,600,700,800},
ytick={0,10,20,30,40,50,60,70,80},
tick label style={font=\tiny},
%xlabel=Split Part Number,
ylabel=Translation Time,
ymin=0,
ymax=80,
xmin=0,
xmax=64,
xtick pos=left,
ytick pos=left,
xtick align=outside,
ytick align=outside,
ybar,
bar width=5pt,
cycle list={fill=black},
width=13cm,
height=4cm
]
%\input{split/histogram_time_sum.64}
\input{figures/parts_time_summary/Algorithm.histogram+Corpus.nist08_dev+Parts.64/plot.tex}
\end{axis}
\end{tikzpicture}
\label{fig:plot-histogram}
%\caption{Total time (in seconds) for each part when split using Algorithm \ref{alg:histogram}.}
%\caption{Translation decoding time (in seconds) of sentences from the NIST OpenMT 2008 Urdu-English task with a decoder configured using a 5-gram language model.}
%\label{fig:histogram-split-times}
}
%\end{figure*}

\subfloat[Algorithm \ref{alg:words} --- \textsc{Words-Split}]{
%\begin{figure*}[!p]
%\centering
\begin{tikzpicture}
\begin{axis}[
xmode=normal,
ymode=normal,
xtick={0,8,16,24,32,40,48,56,64},%data,%{100,200,300,400,500,600,700,800},
ytick={0,10,20,30,40,50,60,70,80},
tick label style={font=\tiny},
%xlabel=Split Part Number,
ylabel=Translation Time,
ymin=0,
ymax=80,
xmin=0,
xmax=64,
xtick pos=left,
ytick pos=left,
xtick align=outside,
ytick align=outside,
ybar,
bar width=5pt,
cycle list={fill=black},
width=13cm,
height=4cm
]
%\input{split/histogram_time_sum.64}
\input{figures/parts_time_summary/Algorithm.words+Corpus.nist08_dev+Parts.64/plot.tex}
\end{axis}
\end{tikzpicture}
\label{fig:plot-words}
%\caption{Total time (in seconds) for each part when split using Algorithm \ref{alg:words}.}
%\caption{Translation decoding time (in seconds) of sentences from the NIST OpenMT 2008 Urdu-English task with a decoder configured using a 5-gram language model.}
%\label{fig:words-split-times}
%\end{figure*}
}

\subfloat[Algorithm \ref{alg:times} --- \textsc{Times-Split}]{
%\begin{figure*}[!p]
%\centering
\begin{tikzpicture}
\begin{axis}[
xmode=normal,
ymode=normal,
xtick={0,8,16,24,32,40,48,56,64},%data,%{100,200,300,400,500,600,700,800},
ytick={0,10,20,30,40,50,60,70,80},
tick label style={font=\tiny},
%xlabel=Split Part Number,
ylabel=Translation Time,
ymin=0,
ymax=80,
xmin=0,
xmax=64,
xtick pos=left,
ytick pos=left,
xtick align=outside,
ytick align=outside,
ybar,
bar width=5pt,
cycle list={fill=black},
width=13cm,
height=4cm
]
%\input{split/histogram_time_sum.64}
\input{figures/parts_time_summary/Algorithm.time+Corpus.nist08_dev+Parts.64/plot.tex}
\end{axis}
\end{tikzpicture}
\label{fig:plot-time}
}
\caption{Total translation time (in \textbf{seconds}) for each part when data from the NIST OpenMT 2008 Urdu-English task is split into 64 parts using each of four algorithms.}
%\caption{Translation decoding time (in seconds) of sentences from the NIST OpenMT 2008 Urdu-English task with a decoder configured using a 5-gram language model.}
\label{fig:time-split-times}
\end{figure*}

>>>>

\documentclass{pbml}
\usepackage{natbib}
\usepackage{thanks-nostar}
\usepackage{subfig}
%\setlength\titlebox{3in}
%\usepackage{naaclhlt2010}
%\usepackage{draftcopy}[all,draft,light,timestamp]
%\usepackage{draftwatermark}
%\usepackage{datetime}
%\usepackage{times}
%\usepackage{latexsym}
%\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
\newcommand\bmmax{1}
\usepackage{bm}
\usepackage{fontspec}
%\usepackage{todonotes}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\usepackage[colorlinks,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{
width=7cm,
compat=1.3,
colormap name=blackwhite
%,bar cycle list name=black white
}
%\SetWatermarkLightness{0.95}
%\SetWatermarkLightness{1}
%\SetWatermarkText{\dmyydate \today, \currenttime}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\begin{figure*}[!p]
\centering
%\subfloat[Algorithm 1 --- \textsc{Naive-Split}]{
\subfloat[Algorithm \protect\ref{alg:naive} --- \textsc{Naive-Split}]{
\begin{tikzpicture}
\begin{axis}[
xmode=normal,
ymode=normal,
xtick={0,8,16,24,32,40,48,56,64},
ytick={0,10,20,30,40,50,60,70,80},
tick label style={font=\tiny},
ylabel=Translation Time,
ymin=0,
ymax=80,
xmin=0,
xmax=64,
xtick pos=left,
ytick pos=left,
xtick align=outside,
ytick align=outside,
ybar,
bar width=5pt,
cycle list={fill=black},
width=13cm,
height=4cm
]
\input{figures/parts_time_summary/Algorithm.naive+Corpus.nist08_dev+Parts.64/plot.tex}
\end{axis}
\end{tikzpicture}
\label{fig:plot-naive}
}

\subfloat[Algorithm \protect\ref{alg:histogram} --- \textsc{Histogram-Split}]{
%\begin{figure*}[!p]
%\centering
\begin{tikzpicture}
\begin{axis}[
xmode=normal,
ymode=normal,
xtick={0,8,16,24,32,40,48,56,64},%data,%{100,200,300,400,500,600,700,800},
ytick={0,10,20,30,40,50,60,70,80},
tick label style={font=\tiny},
%xlabel=Split Part Number,
ylabel=Translation Time,
ymin=0,
ymax=80,
xmin=0,
xmax=64,
xtick pos=left,
ytick pos=left,
xtick align=outside,
ytick align=outside,
ybar,
bar width=5pt,
cycle list={fill=black},
width=13cm,
height=4cm
]
%\input{split/histogram_time_sum.64}
\input{figures/parts_time_summary/Algorithm.histogram+Corpus.nist08_dev+Parts.64/plot.tex}
\end{axis}
\end{tikzpicture}
\label{fig:plot-histogram}
%\caption{Total time (in seconds) for each part when split using Algorithm \ref{alg:histogram}.}
%\caption{Translation decoding time (in seconds) of sentences from the NIST OpenMT 2008 Urdu-English task with a decoder configured using a 5-gram language model.}
%\label{fig:histogram-split-times}
}
%\end{figure*}

\subfloat[Algorithm \protect\ref{alg:words} --- \textsc{Words-Split}]{
%\begin{figure*}[!p]
%\centering
\begin{tikzpicture}
\begin{axis}[
xmode=normal,
ymode=normal,
xtick={0,8,16,24,32,40,48,56,64},%data,%{100,200,300,400,500,600,700,800},
ytick={0,10,20,30,40,50,60,70,80},
tick label style={font=\tiny},
%xlabel=Split Part Number,
ylabel=Translation Time,
ymin=0,
ymax=80,
xmin=0,
xmax=64,
xtick pos=left,
ytick pos=left,
xtick align=outside,
ytick align=outside,
ybar,
bar width=5pt,
cycle list={fill=black},
width=13cm,
height=4cm
]
%\input{split/histogram_time_sum.64}
\input{figures/parts_time_summary/Algorithm.words+Corpus.nist08_dev+Parts.64/plot.tex}
\end{axis}
\end{tikzpicture}
\label{fig:plot-words}
%\caption{Total time (in seconds) for each part when split using Algorithm \ref{alg:words}.}
%\caption{Translation decoding time (in seconds) of sentences from the NIST OpenMT 2008 Urdu-English task with a decoder configured using a 5-gram language model.}
%\label{fig:words-split-times}
%\end{figure*}
}

\subfloat[Algorithm \protect\ref{alg:times} --- \textsc{Times-Split}]{
%\begin{figure*}[!p]
%\centering
\begin{tikzpicture}
\begin{axis}[
xmode=normal,
ymode=normal,
xtick={0,8,16,24,32,40,48,56,64},%data,%{100,200,300,400,500,600,700,800},
ytick={0,10,20,30,40,50,60,70,80},
tick label style={font=\tiny},
%xlabel=Split Part Number,
ylabel=Translation Time,
ymin=0,
ymax=80,
xmin=0,
xmax=64,
xtick pos=left,
ytick pos=left,
xtick align=outside,
ytick align=outside,
ybar,
bar width=5pt,
cycle list={fill=black},
width=13cm,
height=4cm
]
%\input{split/histogram_time_sum.64}
\input{figures/parts_time_summary/Algorithm.time+Corpus.nist08_dev+Parts.64/plot.tex}
\end{axis}
\end{tikzpicture}
\label{fig:plot-time}
}
\caption{Total translation time (in \textbf{seconds}) for each part when data from the NIST OpenMT 2008 Urdu-English task is split into 64 parts using each of four algorithms.}
%\caption{Translation decoding time (in seconds) of sentences from the NIST OpenMT 2008 Urdu-English task with a decoder configured using a 5-gram language model.}
\label{fig:time-split-times}
\end{figure*}
